Synthesis report

### 2020-03-18 analysis/reports/found_all.Rmd
run portal pipeline

Here is the overall distribution of skewness, and if we split based on whether we found all the samples:
```{r skew percentiles}
ggplot(filter(all_di, singletons == F), aes(x = skew_percentile, y =..count.. / sum(..count..))) +
  geom_histogram(bins = 100) +
  theme_bw() +
  geom_hline(yintercept = .01)
ggplot(filter(all_di, singletons == F), aes(x = skew_percentile)) +
  theme_bw() +
  geom_histogram(bins = 100) +
  facet_wrap(vars(found_all), scales = "free_y")
```

@@

ggplot(filter(all_di, singletons == F, found_all), aes(x = log(s0), y = log(n0), color = skew_percentile)) +
  geom_point(alpha = .5) +
  theme_bw() +
  theme(legend.position = "top") + scale_color_viridis_c(option = "plasma", end = .9)

@@

So I'm pretty sure the spike at 0 is the communities with 1 or 2 species, for which we shouldn't be calculating skewness anyway.

```{r binned nparts, fig.dim = c(10,10)}
all_di <- all_di %>%
  mutate(nparts_binned = as.factor(ceiling(log_nparts / 5) * 5))

@@

```{r simpson percentiles}
ggplot(filter(all_di, singletons == F), aes(x = simpson_percentile, y =..count.. / sum(..count..))) +
  geom_histogram(bins = 100) +
  theme_bw() +
  geom_hline(yintercept = .01)

ggplot(filter(all_di, singletons == F), aes(x = simpson_percentile)) +
  theme_bw() +
  geom_histogram(bins = 100) +
  facet_wrap(vars(found_all))

@@

```{r even v s and n, fig.dim = c(10,10)}

ggplot(filter(all_di, singletons == F, found_all), aes(x = log(s0), y = log(n0), color = simpson_percentile)) +
  geom_point(alpha = .5) +
  theme_bw() +
  theme(legend.position = "top") + scale_color_viridis_c(option = "plasma", end = .9)

@@

There is nothing to learn when s0 = 1 or really 2.

@@

ggplot(filter(all_di, !singletons, s0 >= 3), aes(x = simpson_percentile)) +
  geom_histogram(bins = 100) +
  theme_bw() +
  facet_wrap(vars(nparts_binned), scales = "free_y")

@@

```{r nparts and dat, fig.dim = c(15,15), include = F}
for(i in 1:nrow(all_di)) {
  if(as.numeric(levels(all_di$nparts_binned)[as.numeric(all_di$nparts_binned[i])]) >= 50) {
    all_di$nparts_binned[i] <- 50
  }
}

@@

>>>>

Here is the overall distribution of skewness, and if we split based on whether we found all the samples:
```{r skew percentiles}
ggplot(filter(all_di, singletons == F, s0 >= 3), aes(x = skew_percentile, y =..count.. / sum(..count..))) +
  geom_histogram(bins = 100) +
  theme_bw() +
  geom_hline(yintercept = .01)
ggplot(filter(all_di, singletons == F, s0 >= 3), aes(x = skew_percentile)) +
  theme_bw() +
  geom_histogram(bins = 100) +
  facet_wrap(vars(found_all), scales = "free_y")
```

@@

ggplot(filter(all_di, singletons == F, found_all, s0 >= 3), aes(x = log(s0), y = log(n0), color = skew_percentile)) +
  geom_point(alpha = .5) +
  theme_bw() +
  theme(legend.position = "top") + scale_color_viridis_c(option = "plasma", end = .9)

@@

Here is how the histogram changes as we bin the lognparts into 2s:

```{r binned nparts, fig.dim = c(10,10)}
all_di <- all_di %>%
  mutate(nparts_binned = as.factor(ceiling(log_nparts / 2) * 2))

for(i in 1:nrow(all_di)) {
  if(as.numeric(levels(all_di$nparts_binned)[as.numeric(all_di$nparts_binned[i])]) >= 25) {
    all_di$nparts_binned[i] <- 26
  }
}

@@

```{r simpson percentiles}
ggplot(filter(all_di, singletons == F, s0 >= 2), aes(x = simpson_percentile, y =..count.. / sum(..count..))) +
  geom_histogram(bins = 100) +
  theme_bw() +
  geom_hline(yintercept = .01)

ggplot(filter(all_di, singletons == F, s0 >= 2), aes(x = simpson_percentile)) +
  theme_bw() +
  geom_histogram(bins = 100) +
  facet_wrap(vars(found_all))

@@

```{r even v s and n}

ggplot(filter(all_di, singletons == F, found_all, s0 >= 2), aes(x = log(s0), y = log(n0), color = simpson_percentile)) +
  geom_point(alpha = .5) +
  theme_bw() +
  theme(legend.position = "top") + scale_color_viridis_c(option = "plasma", end = .9)

@@

@@

ggplot(filter(all_di, !singletons, s0 >= 2), aes(x = simpson_percentile)) +
  geom_histogram(bins = 100) +
  theme_bw() +
  facet_wrap(vars(nparts_binned), scales = "free_y")

@@

```{r nparts and dat, fig.dim = c(15,15)}
for(i in 1:nrow(all_di)) {
  if(as.numeric(levels(all_di$nparts_binned)[as.numeric(all_di$nparts_binned[i])]) >= 50) {
    all_di$nparts_binned[i] <- 50
  }
}

@@

```{r nparts variability}

ggplot(filter(all_di, !singletons, s0 >= 3, !is.infinite(skew_sd), !is.infinite(skew_mean), nsamples >2), aes(x = log_nparts, y = (skew_sd/skew_mean), color = skew_percentile)) +
  geom_point(alpha = .1) +
  theme_bw() +
  geom_vline(xintercept = 10) +
  scale_color_viridis_c() +
  ylim(-0, 1) +
  xlim(0, 100)

ggplot(filter(all_di, !singletons, s0 >= 3, !is.infinite(simpson_sd), !is.infinite(simpson_sd), nsamples >2), aes(x = log_nparts, y = (simpson_sd/simpson_mean), color = simpson_percentile)) +
  geom_point(alpha = .1) +
  theme_bw() +
  geom_vline(xintercept = 10) +
  scale_color_viridis_c() +
  xlim(0, 100)

```{r mean v sd}

ggplot(filter(all_di, !is.infinite(skew_mean), !is.infinite(skew_sd)), aes(x = skew_mean, y = skew_sd)) +
  geom_point() +
  theme_bw()

all_di <- all_di %>%
  mutate(skew_cv = skew_sd / abs(skew_mean),
         simpson_cv = simpson_sd / abs(simpson_mean))

ggplot(filter(all_di, !is.infinite(skew_mean), !is.infinite(skew_sd)), aes(x = skew_mean, y = skew_sd)) +
  geom_point() +
  theme_bw() +
  scale_color_viridis_c()

ggplot(filter(all_di, !is.infinite(simpson_mean), !is.infinite(simpson_sd)), aes(x = simpson_mean, y = simpson_sd)) +
  geom_point() +
  theme_bw() +
  scale_color_viridis_c()

Mean and sd are correlated.

```{r cv in space}

ggplot(filter(all_di, !singletons, !is.infinite(skew_mean), s0 >= 3, !is.infinite(skew_sd), nparts > 2), aes(log(s0), log(n0), color = log(skew_cv))) +
  geom_point(alpha = .15) +
  scale_color_viridis_c(option = "plasma", end = .9) +
  theme_bw() 
# +
  # facet_wrap(vars(more_than_10))

ggplot(filter(all_di, !singletons, !is.infinite(simpson_mean), s0 >= 2, !is.infinite(simpson_mean), nparts > 2), aes(log(s0), log(n0), color = log(simpson_cv))) +
  geom_point(alpha = .15) +
  scale_color_viridis_c(option = "plasma", end = .9) +
  theme_bw() 
# +
  # facet_wrap(vars(more_than_10))
```

Coefficients of variation for skewness and evenness follow clear S and N gradients.

```{r cv v nparts}
ggplot(filter(all_di, !singletons, !is.infinite(skew_mean), s0 >= 3, !is.infinite(skew_sd), nparts > 2), aes(x = log_nparts, y = skew_cv)) +
  geom_point(alpha = .05) +
  theme_bw() +
  geom_vline(xintercept = 10) +
  xlim(0, 75)

ggplot(filter(all_di, !singletons, !is.infinite(simpson_mean), s0 >= 2, !is.infinite(simpson_mean), nparts > 2), aes(x = log_nparts, y = simpson_cv)) +
  geom_point(alpha = .05) +
  theme_bw() +
  geom_vline(xintercept = 10) +
  xlim(0, 75)
```

The CV scans with nparts and drops off suspiciously right around the same place where the threshold shows up for percentile.

```{r cv v percentile}
all_di <- all_di %>%
  group_by_all() %>%
  mutate(log_nparts_thresh = min(log_nparts, 5)) %>%
  ungroup()

ggplot(filter(all_di, !singletons, !is.infinite(skew_mean), s0 >= 3, !is.infinite(skew_sd), nparts > 2), aes(y = skew_cv, x = skew_percentile, color = log_nparts_thresh)) +
  geom_point(alpha = .1) +
  theme_bw() +
  facet_wrap(vars(more_than_10)) +
  scale_color_viridis_c()

ggplot(filter(all_di, !singletons, !is.infinite(simpson_mean), s0 >= 2, !is.infinite(simpson_sd), nparts > 2), aes(y = simpson_cv, x = simpson_percentile, color = log_nparts_thresh)) +
  geom_point(alpha = .1) +
  theme_bw() +
  facet_wrap(vars(more_than_10)) +
  scale_color_viridis_c() 
```

### 2020-03-18 analysis/reports/synthesis.Rmd
run portal pipeline

# Manipulations
# MACD

```{r load macd}
cache_loc = "macdb"

## Set up the cache and config
db <- DBI::dbConnect(RSQLite::SQLite(), here::here("analysis", "drake", paste0("drake-cache-", cache_loc, ".sqlite")))
cache <- storr::storr_dbi("datatable", "keystable", db)

all_di_macd <- readd(all_di_manip, cache = cache) 
macd_dat <- readd(dat_s_dat_macdb, cache = cache)

DBI::dbDisconnect(db)
rm(cache)

macd_dat <- macd_dat %>%
  group_by(site, dat, singletons, sim, source) %>%
  summarize(s0 = max(rank),
            n0 = sum(abund)) %>%
  ungroup()

all_di_macd <- left_join(all_di_macd, macd_dat, by = c("site", "dat", "singletons", "sim", "source")) %>%
  mutate(log_nparts = log(gmp:::as.double.bigz(nparts)),
         log_nsamples = log(nsamples)) %>%
  mutate(prop_found = exp(log_nsamples - log_nparts)) %>%
  mutate(found_all = prop_found==1)

ggplot(data = all_di, aes(x = log(s0), y = log(n0))) + geom_point(alpha = .1) + geom_point(data = all_di_macd, aes(x = log(s0), y = log(n0)), color = "blue", alpha = .9) + theme_bw()

ggplot(data = filter(all_di, !singletons), aes(x = log(s0), y = log(n0))) + geom_point(alpha = .1) + geom_point(data = filter(all_di_macd, !singletons), aes(x = log(s0), y = log(n0)), color = "blue", alpha = .9) + theme_bw()

Here are the distributions of skew and evenness, overall.

```{r macd overall}

ggplot(data = all_di_macd, aes(x = skew_percentile)) +
  geom_histogram(bins = 100) +
  theme_bw() +
  facet_wrap(vars(found_all), scales = "free_y")

ggplot(data = all_di_macd, aes(x = simpson_percentile)) +
  geom_histogram(bins = 100) +
  theme_bw() +
  facet_wrap(vars(found_all), scales = "free_y")
```

Here is how manipulation affects things:

```{r macd ctrlcomp, fig.dim = c(4,4)}

macd_comparisons <- read.csv(here::here("working-data", "macdb_data", "orderedcomparisons.csv"), header = F, stringsAsFactors = F)

colnames(macd_comparisons) <- c("studyID", "control", "site")
macd_comparisons <- macd_comparisons %>%
  mutate(site = as.character(site), control = as.character(control))

cc_di <- all_di_macd %>%
  filter(singletons == FALSE, treatment == "comparison") %>%
  left_join(macd_comparisons, by = c("studyID", "site")) %>%
  select(dat, site, skew_percentile, simpson_percentile, studyID, control) %>%
  rename(comparison = site) %>%
  mutate(ctrl_skew_percentile = NA,
         ctrl_simpson_percentile = NA)

for(i in 1:nrow(cc_di)) {

  control_row <- filter(all_di_macd, site == cc_di$control[i], singletons == F) %>%
    unique()
  if(nrow(control_row) >0 ) {
    cc_di$ctrl_simpson_percentile[i] <- control_row$simpson_percentile
    cc_di$ctrl_skew_percentile[i] <- control_row$skew_percentile
  }
}

cc_di <- cc_di %>%
  mutate(simpson_change = simpson_percentile - ctrl_simpson_percentile,
         skew_change = skew_percentile - ctrl_skew_percentile)

ggplot(data = cc_di, aes(x = skew_percentile, y = ctrl_skew_percentile)) +
  geom_point(alpha = .5) +
  #  xlim(0, 100) +
  # ylim(0, 100) +
  theme_bw() +
  geom_abline(intercept = 0, slope = 1, color = "green")

ggplot(data = cc_di, aes(x = simpson_percentile, y = ctrl_skew_percentile)) +
  geom_point(alpha = .5) +
  xlim(0, 100) +
  ylim(0, 100) +
  theme_bw() +
  geom_abline(intercept = 0, slope = 1, color = "green")

ggplot(data = cc_di, aes(x = simpson_change)) +
  geom_histogram() +
  theme_bw()

ggplot(data = cc_di, aes(x = skew_change)) +
  geom_histogram() +
  theme_bw()

ggplot(data = cc_di, aes(x = ctrl_simpson_percentile, y = simpson_change)) +
  geom_point(alpha = .3) +
  geom_hline(yintercept = 0) +
  theme_bw()

ggplot(data = cc_di, aes(x = ctrl_skew_percentile, y = skew_change)) +
  geom_point(alpha = .3) +
  geom_hline(yintercept = 0) +
  theme_bw()

print(t.test(cc_di$skew_percentile, cc_di$ctrl_skew_percentile, paired = T)
)
print(t.test(cc_di$simpson_percentile, cc_di$ctrl_simpson_percentile, paired = T)
)

print(wilcox.test(cc_di$skew_percentile, cc_di$ctrl_skew_percentile, paired = T))
print(wilcox.test(cc_di$simpson_percentile, cc_di$ctrl_simpson_percentile, paired = T))

Change is going to be bounded at 100 and 0: you can't go up or down from there. (Another argument for increasing the number of samples?)

# Portal plant manips

```{r load pp}
cache_loc = "portal_plants_manip"

## Set up the cache and config
db <- DBI::dbConnect(RSQLite::SQLite(), here::here("analysis", "drake", paste0("drake-cache-", cache_loc, ".sqlite")))
cache <- storr::storr_dbi("datatable", "keystable", db)

all_di_p<- readd(all_di_manip, cache = cache)

all_di_p <- all_di_p %>%
  mutate(log_nparts = log(gmp:::as.double.bigz(nparts)),
         log_nsamples = log(nsamples)) %>%
  mutate(prop_found = exp(log_nsamples - log_nparts)) %>%
  mutate(found_all = prop_found==1)

DBI::dbDisconnect(db)
rm(cache)
```

Nsamples, singletons

```{r pp overall}
# 
# ggplot(data = all_di_p, aes(x = nsamples)) +
#   geom_histogram(bins = 100) +
#   theme_bw() +
#   geom_vline(xintercept = 2000)
# 
# all_di_p <- filter(all_di_p, nsamples >= 2000)

ggplot(data = all_di_p, aes(x = skew_percentile)) +
  geom_histogram(bins = 100) +
  theme_bw() +
  facet_wrap(vars(found_all), scales = "free_y")

ggplot(data = all_di_p, aes(x = simpson_percentile)) +
  geom_histogram(bins = 100) +
  theme_bw() +
  facet_wrap(vars(found_all), scales = "free_y")
# 
# pp_singletons_effect <- all_di_p %>%
#   select(singletons, skew_percentile, simpson_percentile, year, plot, treatment, season) %>%
#   tidyr::pivot_wider(names_from = singletons, values_from = c("skew_percentile", "simpson_percentile"))
# 
# ggplot(data = pp_singletons_effect, aes(x = skew_percentile_FALSE, y  = skew_percentile_TRUE)) +
#   geom_point(alpha = .1) +
#   geom_abline(intercept = 0, slope = 1, color = "green") +
#   theme_bw()
# 
# 
# ggplot(data = pp_singletons_effect, aes(x = simpson_percentile_FALSE, y  = simpson_percentile_TRUE)) +
#   geom_point(alpha = .1) +
#   geom_abline(intercept = 0, slope = 1, color = "green") +
#   theme_bw()
```

By treatment, season

```{r portal trtmt}
ggplot(data = filter(all_di_p, singletons == F), aes(x = skew_percentile)) +
  geom_histogram(bins = 100) +
  theme_bw() +
  facet_wrap(vars(season, treatment), scales = "free_y")

ggplot(data = filter(all_di_p, singletons == F), aes(x = treatment, y = skew_percentile)) +
  geom_boxplot() +
  theme_bw() +
  facet_wrap(vars(season))

ggplot(data = filter(all_di_p, singletons == F), aes(x = simpson_percentile)) +
  geom_histogram(bins = 100) +
  theme_bw() +
  facet_wrap(vars(season, treatment), scales = "free_y")

ggplot(data = filter(all_di_p, singletons == F), aes(x = treatment, y = simpson_percentile)) +
  geom_boxplot() +
  theme_bw() +
  facet_wrap(vars(season))
```

<!-- By year -->

<!-- ```{r plants year, fig.height = 25, fig.width = 5} -->

<!-- ggplot(data = filter(all_di_p, singletons == F), aes(x = treatment, y = skew_percentile)) + -->
<!--   geom_boxplot() + -->
<!--   theme_bw() + -->
<!--   facet_grid(rows = vars(year), cols = vars(season), scales = "free_y") -->
<!-- ggplot(data = filter(all_di_p, singletons == F), aes(x = treatment, y = simpson_percentile)) + -->
<!--   geom_boxplot() + -->
<!--   theme_bw() + -->
<!--   facet_grid(rows = vars(year), cols = vars(season), scales = "free_y") -->
<!-- ``` -->

Median
```{r pp median, fig.width = 12, fig.height = 12}

pp_median <- all_di_p %>%
  filter(singletons == F) %>%
  group_by(season, year, treatment) %>%
  summarize(skew_percentile = median(skew_percentile),
            simpson_percentile = median(simpson_percentile)) %>%
  ungroup() %>%
  tidyr::pivot_wider(names_from = treatment, values_from = c(skew_percentile, simpson_percentile))

sk_x <- ggplot(data = pp_median, aes(x = skew_percentile_control, y = skew_percentile_exclosure)) +
  geom_point(alpha = .5) +
  facet_wrap(vars(season)) +
  theme_bw() +
  ggtitle("Skew Ctrl v Exclosure") +
  geom_abline(intercept = 0, slope = 1, color = "green") +
  xlim(40, 100) +
  ylim(40, 100)

sk_r <- ggplot(data = pp_median, aes(x = skew_percentile_control, y = skew_percentile_removal)) +
  geom_point(alpha = .5) +
  facet_wrap(vars(season)) +
  theme_bw() +
  ggtitle("Skew Ctrl v Removal") +
  geom_abline(intercept = 0, slope = 1, color = "green") +
  xlim(40, 100) +
  ylim(40, 100)

gridExtra::grid.arrange(grobs = list(sk_x, sk_r), nrow = 2)

sp_x <- ggplot(data = pp_median, aes(x = simpson_percentile_control, y = simpson_percentile_exclosure)) +
  geom_point(alpha = .5) +
  facet_wrap(vars(season)) +
  theme_bw() +
  ggtitle("Simpson Ctrl v Exclosure") +
  geom_abline(intercept = 0, slope = 1, color = "green") +
  xlim(0, 40) +
  ylim(0, 40)

sp_r <- ggplot(data = pp_median, aes(x = simpson_percentile_control, y = simpson_percentile_removal)) +
  geom_point(alpha = .5) +
  facet_wrap(vars(season)) +
  theme_bw() +
  ggtitle("Simpson Ctrl v Removal") +
  geom_abline(intercept = 0, slope = 1, color = "green") +
  xlim(0, 40) +
  ylim(0, 40)

gridExtra::grid.arrange(grobs = list(sp_x, sp_r), nrow = 2)
```

>>>>

<!-- # Manipulations -->
<!-- # MACD -->

<!-- ```{r load macd, include =F} -->
<!-- cache_loc = "macdb" -->

<!-- ## Set up the cache and config -->
<!-- db <- DBI::dbConnect(RSQLite::SQLite(), here::here("analysis", "drake", paste0("drake-cache-", cache_loc, ".sqlite"))) -->
<!-- cache <- storr::storr_dbi("datatable", "keystable", db) -->

<!-- all_di_macd <- readd(all_di_obs, cache = cache)  -->
<!-- all_di_macd_manip <- readd(all_di_manip, cache = cache) -->
<!-- macd_dat <- readd(dat_s_dat_macdb, cache = cache) -->

<!-- DBI::dbDisconnect(db) -->
<!-- rm(cache) -->

<!-- all_di_macd <- all_di_macd %>% -->
<!--   mutate(log_nparts = log(gmp:::as.double.bigz(nparts)), -->
<!--          log_nsamples = log(nsamples)) %>% -->
<!--   mutate(prop_found = exp(log_nsamples - log_nparts)) %>% -->
<!--   mutate(found_all = prop_found==1) -->
<!-- #  -->
<!-- # all_di_macd_manip <- all_di_macd_manip %>% -->
<!-- #   mutate(log_nparts = log(gmp:::as.double.bigz(nparts)), -->
<!-- #          log_nsamples = log(nsamples)) %>% -->
<!-- #   mutate(prop_found = exp(log_nsamples - log_nparts)) %>% -->
<!-- #   mutate(found_all = prop_found==1) -->

<!-- ggplot(data = all_di, aes(x = log(s0), y = log(n0))) + geom_point(alpha = .1) + geom_point(data = all_di_macd, aes(x = log(s0), y = log(n0)), color = "blue", alpha = .9) + theme_bw() -->

<!-- ggplot(data = filter(all_di, !singletons), aes(x = log(s0), y = log(n0))) + geom_point(alpha = .1) + geom_point(data = filter(all_di_macd, !singletons), aes(x = log(s0), y = log(n0)), color = "blue", alpha = .9) + theme_bw() -->

<!-- ``` -->

<!-- Here are the distributions of skew and evenness, overall. -->

<!-- ```{r macd overall, include =F} -->

<!-- ggplot(data = all_di_macd, aes(x = skew_percentile)) + -->
<!--   geom_histogram(bins = 100) + -->
<!--   theme_bw() + -->
<!--   facet_wrap(vars(found_all), scales = "free_y") -->

<!-- ggplot(data = all_di_macd, aes(x = simpson_percentile)) + -->
<!--   geom_histogram(bins = 100) + -->
<!--   theme_bw() + -->
<!--   facet_wrap(vars(found_all), scales = "free_y") -->
<!-- ``` -->

<!-- Here is how manipulation affects things: -->

<!-- ```{r macd ctrlcomp, fig.dim = c(4,4), include =F} -->

<!-- ggplot(data = all_di_macd_manip, aes(x = skew_percentile, y = ctrl_skew_percentile)) + -->
<!--   geom_point(alpha = .5) + -->
<!--   #  xlim(0, 100) + -->
<!--   # ylim(0, 100) + -->
<!--   theme_bw() + -->
<!--   geom_abline(intercept = 0, slope = 1, color = "green") -->

<!-- ggplot(data = all_di_macd_manip, aes(x = simpson_percentile, y = ctrl_skew_percentile)) + -->
<!--   geom_point(alpha = .5) + -->
<!--   xlim(0, 100) + -->
<!--   ylim(0, 100) + -->
<!--   theme_bw() + -->
<!--   geom_abline(intercept = 0, slope = 1, color = "green") -->

<!-- ggplot(data = all_di_macd_manip, aes(x = simpson_change)) + -->
<!--   geom_histogram() + -->
<!--   theme_bw() -->

<!-- ggplot(data = all_di_macd_manip, aes(x = skew_change)) + -->
<!--   geom_histogram() + -->
<!--   theme_bw() -->

<!-- ggplot(data = all_di_macd_manip, aes(x = ctrl_simpson_percentile, y = simpson_change)) + -->
<!--   geom_point(alpha = .3) + -->
<!--   geom_hline(yintercept = 0) + -->
<!--   theme_bw() -->

<!-- ggplot(data = all_di_macd_manip, aes(x = ctrl_skew_percentile, y = skew_change)) + -->
<!--   geom_point(alpha = .3) + -->
<!--   geom_hline(yintercept = 0) + -->
<!--   theme_bw() -->

<!-- print(t.test(all_di_macd_manip$skew_percentile, all_di_macd_manip$ctrl_skew_percentile, paired = T) -->
<!-- ) -->
<!-- print(t.test(all_di_macd_manip$simpson_percentile, all_di_macd_manip$ctrl_simpson_percentile, paired = T) -->
<!-- ) -->

<!-- print(wilcox.test(all_di_macd_manip$skew_percentile, all_di_macd_manip$ctrl_skew_percentile, paired = T)) -->
<!-- print(wilcox.test(all_di_macd_manip$simpson_percentile, all_di_macd_manip$ctrl_simpson_percentile, paired = T)) -->

<!-- ``` -->

<!-- Change is going to be bounded at 100 and 0: you can't go up or down from there. (Another argument for increasing the number of samples?) -->

<!-- # Portal plant manips -->

<!-- ```{r load pp, include = F} -->
<!-- cache_loc = "portal_plants_manip" -->

<!-- ## Set up the cache and config -->
<!-- db <- DBI::dbConnect(RSQLite::SQLite(), here::here("analysis", "drake", paste0("drake-cache-", cache_loc, ".sqlite"))) -->
<!-- cache <- storr::storr_dbi("datatable", "keystable", db) -->

<!-- all_di_p<- readd(all_di_manip, cache = cache)  -->

<!-- all_di_p <- all_di_p %>% -->
<!--   mutate(log_nparts = log(gmp:::as.double.bigz(nparts)), -->
<!--          log_nsamples = log(nsamples)) %>% -->
<!--   mutate(prop_found = exp(log_nsamples - log_nparts)) %>% -->
<!--   mutate(found_all = prop_found==1) -->

<!-- DBI::dbDisconnect(db) -->
<!-- rm(cache) -->
<!-- ``` -->

<!-- Nsamples, singletons -->

<!-- ```{r pp overall, include = F} -->
<!-- #  -->
<!-- # ggplot(data = all_di_p, aes(x = nsamples)) + -->
<!-- #   geom_histogram(bins = 100) + -->
<!-- #   theme_bw() + -->
<!-- #   geom_vline(xintercept = 2000) -->
<!-- #  -->
<!-- # all_di_p <- filter(all_di_p, nsamples >= 2000) -->

<!-- ggplot(data = all_di_p, aes(x = skew_percentile)) + -->
<!--   geom_histogram(bins = 100) + -->
<!--   theme_bw() + -->
<!--   facet_wrap(vars(found_all), scales = "free_y") -->

<!-- ggplot(data = all_di_p, aes(x = simpson_percentile)) + -->
<!--   geom_histogram(bins = 100) + -->
<!--   theme_bw() + -->
<!--   facet_wrap(vars(found_all), scales = "free_y") -->
<!-- #  -->
<!-- # pp_singletons_effect <- all_di_p %>% -->
<!-- #   select(singletons, skew_percentile, simpson_percentile, year, plot, treatment, season) %>% -->
<!-- #   tidyr::pivot_wider(names_from = singletons, values_from = c("skew_percentile", "simpson_percentile")) -->
<!-- #  -->
<!-- # ggplot(data = pp_singletons_effect, aes(x = skew_percentile_FALSE, y  = skew_percentile_TRUE)) + -->
<!-- #   geom_point(alpha = .1) + -->
<!-- #   geom_abline(intercept = 0, slope = 1, color = "green") + -->
<!-- #   theme_bw() -->
<!-- #  -->
<!-- #  -->
<!-- # ggplot(data = pp_singletons_effect, aes(x = simpson_percentile_FALSE, y  = simpson_percentile_TRUE)) + -->
<!-- #   geom_point(alpha = .1) + -->
<!-- #   geom_abline(intercept = 0, slope = 1, color = "green") + -->
<!-- #   theme_bw() -->
<!-- ``` -->

<!-- By treatment, season -->

<!-- ```{r portal trtmt, include =F} -->
<!-- ggplot(data = filter(all_di_p, singletons == F), aes(x = skew_percentile)) + -->
<!--   geom_histogram(bins = 100) + -->
<!--   theme_bw() + -->
<!--   facet_wrap(vars(season, treatment), scales = "free_y") -->

<!-- ggplot(data = filter(all_di_p, singletons == F), aes(x = treatment, y = skew_percentile)) + -->
<!--   geom_boxplot() + -->
<!--   theme_bw() + -->
<!--   facet_wrap(vars(season)) -->

<!-- ggplot(data = filter(all_di_p, singletons == F), aes(x = simpson_percentile)) + -->
<!--   geom_histogram(bins = 100) + -->
<!--   theme_bw() + -->
<!--   facet_wrap(vars(season, treatment), scales = "free_y") -->

<!-- ggplot(data = filter(all_di_p, singletons == F), aes(x = treatment, y = simpson_percentile)) + -->
<!--   geom_boxplot() + -->
<!--   theme_bw() + -->
<!--   facet_wrap(vars(season)) -->
<!-- ``` -->

<!-- <!-- By year --> -->

<!-- <!-- ```{r plants year, fig.height = 25, fig.width = 5} --> -->

<!-- <!-- ggplot(data = filter(all_di_p, singletons == F), aes(x = treatment, y = skew_percentile)) + --> -->
<!-- <!--   geom_boxplot() + --> -->
<!-- <!--   theme_bw() + --> -->
<!-- <!--   facet_grid(rows = vars(year), cols = vars(season), scales = "free_y") --> -->
<!-- <!-- ggplot(data = filter(all_di_p, singletons == F), aes(x = treatment, y = simpson_percentile)) + --> -->
<!-- <!--   geom_boxplot() + --> -->
<!-- <!--   theme_bw() + --> -->
<!-- <!--   facet_grid(rows = vars(year), cols = vars(season), scales = "free_y") --> -->
<!-- <!-- ``` --> -->

<!-- Median -->
<!-- ```{r pp median, fig.width = 12, fig.height = 12, include =F} -->

<!-- pp_median <- all_di_p %>% -->
<!--   filter(singletons == F) %>% -->
<!--   group_by(season, year, treatment) %>% -->
<!--   summarize(skew_percentile = median(skew_percentile), -->
<!--             simpson_percentile = median(simpson_percentile)) %>% -->
<!--   ungroup() %>% -->
<!--   tidyr::pivot_wider(names_from = treatment, values_from = c(skew_percentile, simpson_percentile)) -->

<!-- sk_x <- ggplot(data = pp_median, aes(x = skew_percentile_control, y = skew_percentile_exclosure)) + -->
<!--   geom_point(alpha = .5) + -->
<!--   facet_wrap(vars(season)) + -->
<!--   theme_bw() + -->
<!--   ggtitle("Skew Ctrl v Exclosure") + -->
<!--   geom_abline(intercept = 0, slope = 1, color = "green") + -->
<!--   xlim(40, 100) + -->
<!--   ylim(40, 100) -->

<!-- sk_r <- ggplot(data = pp_median, aes(x = skew_percentile_control, y = skew_percentile_removal)) + -->
<!--   geom_point(alpha = .5) + -->
<!--   facet_wrap(vars(season)) + -->
<!--   theme_bw() + -->
<!--   ggtitle("Skew Ctrl v Removal") + -->
<!--   geom_abline(intercept = 0, slope = 1, color = "green") + -->
<!--   xlim(40, 100) + -->
<!--   ylim(40, 100) -->

<!-- gridExtra::grid.arrange(grobs = list(sk_x, sk_r), nrow = 2) -->

<!-- sp_x <- ggplot(data = pp_median, aes(x = simpson_percentile_control, y = simpson_percentile_exclosure)) + -->
<!--   geom_point(alpha = .5) + -->
<!--   facet_wrap(vars(season)) + -->
<!--   theme_bw() + -->
<!--   ggtitle("Simpson Ctrl v Exclosure") + -->
<!--   geom_abline(intercept = 0, slope = 1, color = "green") + -->
<!--   xlim(0, 40) + -->
<!--   ylim(0, 40) -->

<!-- sp_r <- ggplot(data = pp_median, aes(x = simpson_percentile_control, y = simpson_percentile_removal)) + -->
<!--   geom_point(alpha = .5) + -->
<!--   facet_wrap(vars(season)) + -->
<!--   theme_bw() + -->
<!--   ggtitle("Simpson Ctrl v Removal") + -->
<!--   geom_abline(intercept = 0, slope = 1, color = "green") + -->
<!--   xlim(0, 40) + -->
<!--   ylim(0, 40) -->

<!-- gridExtra::grid.arrange(grobs = list(sp_x, sp_r), nrow = 2) -->
<!-- ``` -->

```{r nparts v rov}

all_di_plot <- filter(all_di, !singletons)

ggplot(all_di_plot, aes(x = log_nparts, y = simpson_mean)) +
  geom_point(alpha = .1) +
  theme_bw() +
  geom_vline(xintercept = 10)

ggplot(all_di_plot, aes(x = log_nparts, y = simpson_sd)) +
  geom_point(alpha = .1) +
  theme_bw() +
  geom_vline(xintercept = 10)

ggplot(all_di_plot, aes(x = log_nparts, y = abs(simpson_sd/simpson_mean))) +
  geom_point(alpha = .1) +
  theme_bw() +
  geom_vline(xintercept = 10)

ggplot(all_di_plot, aes(x = abs(simpson_sd/simpson_mean), y = simpson_percentile, color = log_nparts > 10)) +
  geom_point(alpha = .05) +
  theme_bw() +
  scale_color_viridis_d(end = .8)

ggplot(filter(all_di_plot, s0 > 3, !is.infinite(skew_mean), !is.infinite(skew_sd)), aes(x = log_nparts, y = skew_mean)) +
  geom_point(alpha = .1) +
  theme_bw() +
  geom_vline(xintercept = 10)

ggplot(filter(all_di_plot, s0 > 3, !is.infinite(skew_mean), !is.infinite(skew_sd)), aes(x = log_nparts, y = skew_sd)) +
  geom_point(alpha = .1) +
  theme_bw() +
  geom_vline(xintercept = 10)

ggplot(filter(all_di_plot, s0 > 3, !is.infinite(skew_mean), !is.infinite(skew_sd)), aes(x = log_nparts, y = abs(skew_sd/skew_mean))) +
  geom_point(alpha = .1) +
  theme_bw() +
  geom_vline(xintercept = 10)

ggplot(filter(all_di_plot, s0 > 3, !is.infinite(skew_mean), !is.infinite(skew_sd)), aes(x = abs(skew_sd/skew_mean), y = skew_percentile, color = log_nparts > 10)) +
  geom_point(alpha = .05) +
  theme_bw() +
  scale_color_viridis_d(end = .8) +
  xlim(0,4)
```
